---
title: "test1"
format: html
editor: visual
---

### Week 1 Exercise Part B 

#### To generate 100 values from a log-normal distribution

```{r}
library(ggplot2)
set.seed(33)
sampled_values <- rlnorm(100,5,0.5)

```

#### Linear scale histogram

```{r}
# Create a histogram of the sampled data on a linear scale
linear_plot <- ggplot(data.frame(sampled_values), aes(x = sampled_values)) +
  geom_histogram(binwidth = diff(range(sampled_values)) / 30, 
                 fill = "skyblue", 
                 color = "black") +
  labs(title = "Histogram of Sampled Data on Linear Scale",
       x = "Sampled Values",
       y = "Frequency")
print(linear_plot)
```

Form the plot, we can find that most data under 200 and very few data more than 220.

#### Log scale histgram

```{r}
# Create a histogram of the sampled data on a log scale
log_plot <- ggplot(data.frame(sampled_values), aes(x = sampled_values)) +
  geom_histogram(binwidth = diff(log10(range(sampled_values))) / 30, 
                 fill = "skyblue", 
                 color = "black") +
  scale_x_log10() +
  labs(title = "Histogram of Sampled Data on Log Scale",
       x = "Sampled Values (Log Scale)",
       y = "Frequency")
print(log_plot)
```

Because we changed linear to log scale, we have a very different shape. Most data is around 100-300. Also values smaller than 100 and values bigger than 300 don't have a big difference.

#### Violin plot

```{r}
# Create a violin plot of the sampled data
violin_plot <- ggplot(data.frame(sampled_values), aes(x = "", y = sampled_values)) +
  geom_violin(fill = "skyblue", color = "black") +
  labs(title = "Violin Plot of Sampled Data",
       x = "",
       y = "Sampled Values") +
  theme_minimal()
print(violin_plot)
```

From the violin plot, we can know the data shape directly.

#### To get the mean and standard deviation

```{r}
summary(sampled_values)
```

```{r}
sd(sampled_values)
```

The mean of the 100 values is 174.03 and the standard deviation is 96.67352.
